upwell_IDX

### 2019-08-12 upwell_IDX.Rmd
working process

# Determining the upwelling indeces by changing the angle for each of the sites

@@

wind_angle <- wind_daily %>% 
  dplyr::rename(site = sites) %>% 
  left_join(south_africa_away_wide[,c(2,21)], by = "site") %>% 
  dplyr::rename(coast_angle = heading)

##### Do this
wind_UI <- wind_daily %>% 
  mutate(ui.saws = mean_speed * (cos(dir_circ - coast_angle))) %>% 
  drop_na

index <- wind_UI %>% 
  group_by(sites) %>% 
  select("date", "ui.saws") %>% 
  mutate(saws.condition = ifelse(ui.saws < 12.5, "upwelling"))

>>>>

You can then use the exceedence() function from heatwaveR to check for consecutive numbers of days at or above whatever the UI value is meant to be at 
Sounds good. Good luck!

@@

wind_angle <- wind_daily %>% 
  dplyr::rename(site = sites) %>% 
  left_join(south_africa_away_wide[,c(2,21)], by = "site") %>% 
  dplyr::rename(coast_angle = heading) %>% 
  mutate(ui.saws = mean_speed * (cos(dir_circ - coast_angle))) %>% 
  drop_na

# index <- wind_UI %>% 
#   group_by(sites) %>% 
#   select("date", "ui.saws") %>% 
#   mutate(saws.condition = ifelse(ui.saws < 12.5, "upwelling"))
```
